---
title: ''
author: "Manmeet Bains"
date: "August 19, 2018"
output: pdf_document
---
```{r}
library(vcd)
library(vcdExtra)
```

```{r}
data("DanishWelfare", package="vcd")
```

#1.	Find the total number of cases represented in this table.
```{r}
sum(DanishWelfare$Freq)
```
# There are 5144 casws in this Table.





#2.	In this form, the variables Alcohol and Income should arguably be considered ordered factors. Change them to make them ordered.

```{r}
str(DanishWelfare)
```
```{r}
ordered(DanishWelfare$Alcohol)
```

```{r}
ordered(DanishWelfare$Income)
```



# 3.	Convert this data frame to table form, DanishWelfare.tab, a 4-way array containing the frequencies with appropriate variable names and level names.
```{r}
DanishWelfare.tab <- as.data.frame(DanishWelfare)
xtabs(Freq ~ DanishWelfare.tab$Alcohol+DanishWelfare.tab$Income+DanishWelfare.tab$Status+DanishWelfare.tab$Urban, data = DanishWelfare.tab)
```


# 4.The variable Urban has 5 categories. Find the total frequencies in each of these. How would you collapse the table to have only two categories, City, Non-city?
```{r}
table(DanishWelfare.tab$Urban)
```


```{r}
tab1 <- xtabs(Freq ~ Alcohol + Income + Status+Urban, data=DanishWelfare)
structable(tab1)

tab2 <- collapse.table(tab1,
Urban=c("Non-City", "Non-City", "City", "City", "Non-City"))
structable(tab2)
```














